The Shape and Color of Politics

### 2023-10-31 chapter_2/src/slides/color-book.qmd
updating slides
working on the slides some more

![Aaron Bashir (R), PA-3](../../assets/slides/imgs/bashir.webp){#fig-bashir .absolute left=0 top=100}
![Dwight Evans (D), PA-2](../../assets/slides/imgs/evans.webp){#fig-evans .absolute right=0 bottom=100}

@@

@@

![[1860s Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}

@@

# What do we know so far?

@@

<!--
## The study of visuals in politics

![[@bucy_editors_2021]](../../assets/slides/imgs/bucy_joo.png)

![](../../assets/slides/imgs/dan_arendt.png){.absolute bottom=0 left=0}
![](../../assets/slides/imgs/lindholm_et-al.png){.absolute top=200 left=0}
![](../../assets/slides/imgs/nina_et-al.png){.absolute top=0 left=0}

![[@schloss_politics_2014]](../../assets/slides/imgs/schloss_palmer.png){.absolute top=0 height=400}
![[@williams_whats_2022]](../../assets/slides/imgs/williams_et-al.png){.absolute bottom=200 right=0 height=400}
![[@casiraghi_colors_2022]](../../assets/slides/imgs/casiraghi_et-al.png){.absolute bottom=0 right=0 height=400}

-->
## A snap-judgment model of **visual** political information processing

@@

## Study 1

### Motivation of Study

@@

- Do these associations have systematic influences on campaign strategy? (Study 1)
- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)

### Measurement: How much red and blue do campaigns use?

### Measurement: What is the partisan composition of the district?

### Do campaigns use a different proportion of the colors red and blue in different constituency compositions?

@@

@@

- <span style="color: #616A6B"> How do colors convey political information and effect individual attitudes? </span>
- How do colors influence political deliberation?
- How do colors influence neighborhood evaluations?

>>>>

- Motivation of the project
- A snap-judgment model of politically-relevant information processing
- An experiment
- Is the world consistent with the snap-judgement model?
- The broader book project
- Q&A

### Yard signs are simple, yet effective forms of information

![Highway Yard Sign](../assets/img/highway_yardsign.jpg)

### Pre-test: Perceptions of candidate's party affiliation depends on the color of the yard sign

@@

### Colors can convey identity

@@

![[1860's Republican Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}

@@

# What do we know so far about how we process political information?

### Evaluation of political information happens automatically, and in a motivated manner

@@

## A snap-judgment model of **visual** political information processing

@@

@@

- <span style="color: #616A6B">Motivation of the project</span>
- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
- An experiment
- Is the world consistent with the snap-judgement model?
- The broader book project
- Q&A

## Experiment

@@

### Do practitioners think of color when designing yard signs?

### Campaigns use the colors more or less red and blue depending on partisan composition of electoral district

#### DV: the amount of red and blue in political yard signs

#### IV: partisan composition of the district

### More blue on the yard signs in Democratic strongholds

### More red on the yard signs in Republican strongholds

@@

- <span style="color: #616A6B">How do colors convey political information and effect individual attitudes? </span>
- How do colors influence political deliberation?
- How do colors influence neighborhood evaluations?
